Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-05 paper.tex
Start talking about different delegation schemes
Add reference on QFHE
Need to redo this reference to reflect its acceptance to FOCS though
start describing existing schemes

@@

\section{The Scheme}

Here we describe the scheme between the classical client and an honest quantum server.
Let $x$ be the client's input, and $U_T...U_1$ be the circuit to evaluate.

@@

\subsection{Reduction to 2-local Hamiltonians}

Then we reduce the circuit to an instance of 2-local Hamiltonian. This reduction is mostly based on \cite{quant-ph/0406180}.

@@

>>>>

TODO (maybe don't assume universality?)

@@

In \cite{1804.01082}, a verifiable scheme is proposed. In \cite{1708.02130}, a blind scheme is proposed. (TODO just make this CPA or whatever it actually is...) We propose a verifiable scheme with long output which can also be made blind.

TODO check where does \cite{arXiv:1904.06320} fit in.

\section{Long Output scheme}

Here we describe the scheme between the classical client and an honest quantum server. We mostly follow the logic in \cite{1804.01082}. We first follow \cite{quant-ph/0406180} to reduce the problem to an instance of local Hamiltonian.
Let $x$ be the client's input, and $U_T...U_1$ be the circuit to evaluate.

@@

@@

	\bibitem{1708.02130}
	Urmila Mahadev.
	\newblock Classical Homomorphic Encryption for Quantum Circuits, 2017;
	\newblock arXiv:1708.02130.
